Measuring Software Ticket Quality using Statistical Analysis

### 2017-12-13 proposal/mprop.tex
Add first section of the introduction

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Software Ticket Quality}
\author{Andrei-Mihai Nicolae}
\date{December 18th 2017}
\maketitle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\section{Introduction}\label{intro}

% 2 - 3 pages tops

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Measuring Software Ticket Quality using Statistical Analysis}
\author{Andrei-Mihai Nicolae}
\date{December 18th 2017}
\maketitle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\section{Introduction}\label{intro}
% 2 - 3 pages tops

Software engineering, compared to other engineering fields, such as
mechanical or electrical engineering, is much more abstract - while 
performing maintenance on a car engine or on some electric panel,
you can actually touch the components, they are physical. However, in
computer science and the engineering of software, you cannot see the whole picture.
Of course one can actually open up a laptop or PC and see and touch the
components, but the software, what is actually displayed to the user, 
is just characters in some file that gets compiled/interpreted to machine
code by other components which run on the operating system that, in turn,
can communicate with the kernel (i.e. the component that sits exactly
between the OS and the hardware) and perform the final step - send 
different 1s and 0s encoded into electrical signals to the CPU and various
other hardware components.

Having discussed about the high level of abstraction computers expose to 
their human operators, developing software that runs and performs as expected
in agreement with its requirements is not trivial. Thus, developers have
created software called \emph{issue tracking systems} that can manage
and track \emph{tickets}, which can take various forms, such as bug 
reports, feature requests etc. The aforementioned tickets can vary greatly
and issue tracking systems usually allow developers to include many 
types of information, such as:
  \begin{itemize}
    \item stack traces;
    \item steps to reproduce a bug;
    \item summary and description;
    \item story points (e.g. how many units of time does it take one
      developer to mark the ticket as resolved or completed).
  \end{itemize}

Thus, a still unresolved software engineering issue is how can one create
valuable, high quality tickets?
